A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-11 main.tex
Format by vim-latex.

$\longrightarrow_\beta$ is normal $\beta-$reduction in lambda calculus.
$\longrightarrow_\blacklozenge$ means that when a quoted code is unquoted, it becomes the original code.
$\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
where $\epsilon$ is substituted to the stage variable.
Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD.
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
$\%_\alpha$, the symbol for CSP, is disappeared when $\epsilon$ is substituted to $\alpha$.
$\TB_\alpha$ and $\TBL_\alpha$ is disappeared in the same way as $\%_\alpha$.

@@

\subsubsection{Type Equivalence Rules\\}

@@

	\begin{figure}
		\begin{center}
			\infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs} \\[2mm]
			\infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp} \\[2mm]
				\infrule{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}{\textsc{QT-$\TW$}}\andalso
				\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}}{\textsc{QT-Csp}} \\[2mm]
				\infrule{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A}{\textsc{QT-Gen}} \\[2mm]
				\infrule{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A}{\textsc{QT-Refl}} \andalso
				\infrule{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A}{\textsc{QT-Sym}} \\[2mm]
				\infrule{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}{\textsc{QT-Trans}}
				\caption{Type Equivalence Rules}
				\label{fig:type-equivalence-rules}
				\end{center}
				\end{figure}

>>>>

  $\longrightarrow_\beta$ is ordinary $\beta-$reduction in lambda calculus.
  $\longrightarrow_\blacklozenge$ means that when a code fragment is escaped, it becomes the original code.
  $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
  where $\epsilon$ is substituted to the stage variable.
  Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD.
  There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
  $\%_\alpha$, the symbol for CSP, is disappeared when $\epsilon$ is substituted to $\alpha$.
  $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.

@@

  \subsubsection{Type Equivalence Rules}

@@

  \begin{figure}
      \begin{center}
          \infrule{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V \rho \E \pi :: *@A}{\G\V\Pi x:\tau.\rho \E \Pi x:\sigma.\pi :: *@A}{\QTAbs } \\[2mm]
          \infrule{\G\V \tau \E \sigma :: (\Pi x:\rho.K)@A \andalso \G\V M \E N : \rho @A}{\G\V \tau\ M \E \sigma\ N :: K[x \mapsto M]@A}{\QTApp } \\[2mm]
          \infrule{\G\V \tau \E \sigma :: *@{A\alpha}}{\G\V \TW_{\alpha} \tau \E \TW_{\alpha} \sigma :: *@A}{\textsc{QT-$\TW$}}\andalso
          \infrule{\G\V \tau \E \sigma :: K@A}{\G\V \tau \E \sigma :: K@{A\alpha}}{\textsc{QT-Csp}} \\[2mm]
          \infrule{\G\V \tau \E \sigma :: *@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V \forall\alpha.\tau \E  \forall\alpha.\sigma :: *@A}{\textsc{QT-Gen}} \\[2mm]
          \infrule{\G\V \tau::K@A}{\G\V \tau\E\tau :: K@A}{\textsc{QT-Refl}} \andalso
          \infrule{\G\V \tau \E \sigma :: K@A}{\G\V \sigma \E \tau :: K@A}{\textsc{QT-Sym}} \\[2mm]
          \infrule{\G\V \tau \E \sigma :: K@A \andalso \G\V \sigma \E \rho  :: K@A}{\G\V \tau \E \rho  :: K@A}{\textsc{QT-Trans}}
          \caption{Type Equivalence Rules}
          \label{fig:type-equivalence-rules}
      \end{center}
  \end{figure}
